Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
added citations for model discussion
added education/moved links to references

output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

•	https://www.pewresearch.org/fact-tank/2014/07/09/the-politics-of-american-generations-how-age-affects-attitudes-and-voting-behavior/
•	https://www.texasobserver.org/young-voters-texas-2020/
•	https://www.mckinsey.com/featured-insights/employment-and-growth/poorer-than-their-parents-a-new-perspective-on-income-inequality#
•	https://pubmed.ncbi.nlm.nih.gov/10750310/

@@

•	https://www.nytimes.com/2016/10/08/us/donald-trump-tape-transcript.html
•	https://www.bbc.com/news/election-us-2020-54512678
•	https://cawp.rutgers.edu/sites/default/files/resources/genderdiff.pdf

@@

@@

>>>>

output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
link-citations: yes
---

@@

@@

@@

Figure 4 outlines the difference in voting based on the voter’s level of education. The first thing of note is that there is a slight majority for Trump for those who have not attended university. However, the difference is so small that it’s essentially equal from a top down perspective. In comparison, those who have attended university tend to support Biden. There are a few reasons this could be the case. One is the notion that universities “make” people more left-wing. Whether or not this is truly the case, and if so for what reason, aside, this is a commonly held belief. However, this may not be the sole reason why such a divide exists. In recent years, conservatives have majorly considered higher education to have a negative effect on the country. (pewsocial) Inferring from this, conservatives are thus less likely to attend university or view university with a particularly positive perspective than their left-wing counterparts.

The difference between those who support Trump and those who support Biden for voters who have attended university is not insignificant, but in relation to those previously discussed, it may seem inconsequential.  That said, it’s still an important finding if not for the fact that based on Figure 8, we can see that the majority of the population has attended university. As the majority of post-secondary attendees support Biden and it’s relatively equal for those who haven’t, this naturally supports a Biden victory.

@@

•	https://www.pewresearch.org/fact-tank/2014/07/09/the-politics-of-american-generations-how-age-affects-attitudes-and-voting-behavior/
•	https://www.texasobserver.org/young-voters-texas-2020/
•	https://www.mckinsey.com/featured-insights/employment-and-growth/poorer-than-their-parents-a-new-perspective-on-income-inequality#
•	https://pubmed.ncbi.nlm.nih.gov/10750310/
•	https://www.nytimes.com/2016/10/08/us/donald-trump-tape-transcript.html
•	https://www.bbc.com/news/election-us-2020-54512678
•	https://cawp.rutgers.edu/sites/default/files/resources/genderdiff.pdf
https://www.pewsocialtrends.org/essay/the-growing-partisan-divide-in-views-of-higher-education/
